Inference methods comparison for the simplified Naomi model

### 2023-04-13 src/naomi-simple_compare/comparison.Rmd
Look at results comparing PCA-AGHQ k = 3, s = 8 to TMB #22

@@

Nodes where `TMB` beats `adam`:

```{r}
ks_comparison(ks_summary, method1 = "adam", method2 = "TMB", 10)
```

```{r}
histogram_and_ecdf(par = "u_alpha_xs", i = 18)
histogram_and_ecdf(par = "u_alpha_xs", i = 29)
histogram_and_ecdf(par = "ui_anc_alpha_x", i = 29)
```

Nodes where `adam` beats `TMB`:

```{r}
ks_comparison(ks_summary, method1 = "TMB", method2 = "adam", 10)  
```

```{r}
histogram_and_ecdf(par = "log_or_gamma", i = 18)
histogram_and_ecdf(par = "ui_anc_rho_x", i = 10)
histogram_and_ecdf(par = "log_or_gamma", i = 1)
```

>>>>

ks_summary %>%
  filter(Type != "Hyper") %>%
  summary_ks_plot("TMB", "aghq")

@@

Nodes where `TMB` beats `aghq`:

```{r}
ks_comparison(ks_summary, method1 = "aghq", method2 = "TMB", 10)
```

```{r}
histogram_and_ecdf(par = "ui_anc_alpha_x", i = 18)
histogram_and_ecdf(par = "u_alpha_xs", i = 18)
histogram_and_ecdf(par = "ui_anc_alpha_x", i = 29)
```

Nodes where `aghq` beats `TMB`:

```{r}
ks_comparison(ks_summary, method1 = "TMB", method2 = "aghq", 10)  
```

```{r}
histogram_and_ecdf(par = "us_alpha_xs", i = 30)
histogram_and_ecdf(par = "us_alpha_xs", i = 31)
histogram_and_ecdf(par = "us_alpha_xs", i = 26)
```
